Data Management for LSST Special Programs

### 2024-04-05 ap_spcs.tex
change step 3 in ddf

Step 3. Special Processing with reconfigured pipelines. \\
First, a template image of appropriate depth for ``nightly" difference imaging is created.
At the end of each nightly sequence of observations, a pipeline based on recongfigured 
components of the LSST Science Pipelines could be automatically triggered.
This pipeline creates nightly coadds in each filter and runs DIA using the template.
Alerts are \emph{not} produced, but unique and separate catalogs with the same format
as {\tt DiaObject} and {\tt DiaSource} could be updated within 24 hours (not a requirement).
Instead of running daily, this processing might run weekly instead (TBD).
At the end of each season, deeply coadded images that include all of the DDF's visits 
from all years are re-generated, along with a separate {\tt Object}-like catalog.
All images and catalogs are stored in separate butler collections and TAP tables from
the Main Survey data products.

>>>>

Step 3. Special Processing with reconfigured pipelines. \\
First, a template image of appropriate depth for ``nightly" difference imaging is created.
At the end of each nightly sequence of observations, a pipeline based on recongfigured 
components of the LSST Science Pipelines could be automatically triggered.
This pipeline creates nightly coadds in each filter and runs DIA using the template.
Unique and separate catalogs with the same format
as {\tt DiaObject} and {\tt DiaSource} could be updated within, e.g., 24 hours (not a requirement),
and alert packets could be created and produced (with a flag set to identify them
as longer-latency alerts from nightly stacked DDF images).
Instead of running daily, this processing might run weekly instead (TBD).
At the end of each season, deeply coadded images that include all of the DDF's visits 
from all years are re-generated, along with a separate {\tt Object}-like catalog.
All images and catalogs are stored in separate butler collections and TAP tables from
the Main Survey data products.
